Viscous Transport in Eroding Porous Media

### 2019-05-09 docs/transport/erosion_transport.tex
doing the transport paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Double-Layer
Potential}
The Stokes double-layer potential~\eqref{eqn:stokesDLP} can be
decomposed as
\begin{align}
  \DDD[\eeta](\xx) &= 
    \frac{1}{2\pi} \int_{\Gamma} 
      \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
    \frac{1}{2\pi} \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
    &- \frac{1}{2\pi} x_1 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
    \frac{1}{2\pi} x_2 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
\end{align}
All these integrals but the first are a gradient of a Laplace layer
potential with the density functions $\eta_1$, $\eta_2$, and $\yy \cdot
\eeta$.  In addition, each component of the first integral can be
written as a Cauchy integral with a complex-valued
densities~\cite{bar-wu-vee2015}.  Therefore, the Stokes double-layer
potential can be written as five Cauchy integrals and their derivatives
with the density functions $\yy \cdot \eeta$, $\eta_1$, and $\eta_2$.
The individual velocity components are
\begin{align}
  u_1(\xx) &= \Re (v[\tau_1](x)) + \Re (v'[\yy\cdot\eeta](x)) 
           -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)),\\
  u_2(\xx) &= \Re (v[\tau_2](x)) - \Im (v'[\yy\cdot\eeta](x)) 
       +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
\end{align}
where
\begin{align} 
  \tau_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad \text{and} \quad
  \tau_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
\end{align}
and $n \in \CC$ is the complex representation of $\nn \in \RR^2$

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Shear Stress}
To compute the rate of erosion, we must compute the shear stress of the
double-layer potential
\begin{align}
  \tau(\xx) = \left(\nabla \DDD[\eeta](\xx) + 
    \nabla^T \DDD[\eeta](\xx) \right) \nn \cdot \ss,
\end{align}
where $\nn$ and $\ss$ are the unit normal and tangent vectors at $\xx$,
respectively.  Each term of the gradient of the velocity field can be
written in terms of Cauchy integrals as
\todo[inline]{not clear enough how we got these equations.  Need to show
how we do one of them and say the rest are calculated similarly.}
\begin{align}
  \pderiv{u_1}{x_1}(\xx) &= \Re (v'[\tau_1](x)) + 
    \Re (v''[\yy\cdot\eeta](x)) - \Re (v'[\eta_1](x)) - 
    x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x)), \\
  \pderiv{u_1}{x_2}(\xx) &= - \Im (v'[\tau_1](x)) - 
    \Im (v''[\yy\cdot\eeta](x)) + \Im (v''[\eta_1](x)) - 
    \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)), \\
  \pderiv{u_2}{x_1}(\xx) &= \Re (v'[\tau_2](x)) - 
    \Im (v''[\yy\cdot\eeta](x)) + \Im (v'[\eta_1](x)) +
    x_1\Im (v''[\eta_1](x)) + x_2\Im (v''[\eta_2](x)), \\
  \pderiv{u_2}{x_2}(\xx) &= -\Im (v'[\tau_2](x)) - 
    \Re (v''[\yy\cdot\eeta](x)) + x_1\Re (v''[\eta_1](x)) +
    \Im (v'[\eta_2](x)) + x_2\Re (v''[\eta_2](x)).
\end{align}
\todo[inline]{S-H: last term seems to be missing an $x_1$.  Some of the
other terms seem to be a bit off.  It might be partially my fault from
when I updated some of the tex.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Vorticity}
Having calculated all derivatives of the double-layer potential, the
vorticity can written in terms of Cauchy integrals.  In particular
\begin{align}
  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
\end{align}
\todo[inline]{For S-H to fill in}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barycentric Quadrature for $v''(x)$}
While accurate quadrature rules for $v(x)$ and $v'(x)$ have already been
developed~\cite{bar-wu-vee2015}, this work requires a similar quadrature
rule for $v''(x)$.  We mimic the approach developed
in~\cite{bar-wu-vee2015} by starting with the identities
\todo[inline]{S-H: How do we get these identities?}
\begin{alignat}{3}
  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy, &&x \in \Omega, \\
  0 &= \frac{1}{2\pi i}\int_{\Gamma}
    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
\end{alignat}
{\color{red}
and the quadrature formulations are
\begin{alignat}{3}
  v''(x) &\approx
    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
\end{alignat}
where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Double-Layer
Potential}
The Stokes double-layer potential~\eqref{eqn:stokesDLP} can be
decomposed as
\begin{align}
  \DDD[\eeta](\xx) &= 
    \frac{1}{2\pi} \int_{\Gamma} 
      \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
    \frac{1}{2\pi} \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
    &- \frac{1}{2\pi} x_1 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
    \frac{1}{2\pi} x_2 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
\end{align}
All these integrals but the first are a gradient of a Laplace layer
potential with the density functions $\eta_1$, $\eta_2$, and $\yy \cdot
\eeta$.  In addition, each component of the first integral can be
written as a Cauchy integral with a complex-valued
densities~\cite{bar-wu-vee2015}.  Therefore, the Stokes double-layer
potential can be written as five Cauchy integrals and their derivatives
with the density functions $\yy \cdot \eeta$, $\eta_1$, and $\eta_2$.
The individual velocity components are
\begin{align}
  u_1(\xx) &= \Re (v[\tau_1](x)) + \Re (v'[\yy\cdot\eeta](x)) 
           -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \label{eqn:cauchy1}\\
  u_2(\xx) &= \Re (v[\tau_2](x)) - \Im (v'[\yy\cdot\eeta](x)) 
       +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
\end{align}
where
\begin{align} 
  \tau_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad \text{and} \quad
  \tau_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
\end{align}
and $n \in \CC$ is the complex representation of $\nn \in \RR^2$

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Shear Stress}
To compute the rate of erosion, we must compute the shear stress of the
double-layer potential
\begin{align}
  \tau(\xx) = \left(\nabla \DDD[\eeta](\xx) + 
    \nabla^T \DDD[\eeta](\xx) \right) \nn \cdot \ss,
\end{align}
where $\nn$ and $\ss$ are the unit normal and tangent vectors at $\xx$,
respectively.  Each term of the gradient of the velocity field can be
written in terms of Cauchy integrals as
\todo[inline]{not clear enough how we got these equations.  Need to show
how we do one of them and say the rest are calculated similarly.}
\begin{align}
  \pderiv{u_1}{x_1}(\xx) &= \Re (v'[\tau_1](x)) + 
    \Re (v''[\yy\cdot\eeta](x)) - \Re (v'[\eta_1](x)) - 
    x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x)), \label{eqn:pderiv1} \\
  \pderiv{u_1}{x_2}(\xx) &= - \Im (v'[\tau_1](x)) - 
    \Im (v''[\yy\cdot\eeta](x)) + x_1\Im (v''[\eta_1](x)) - 
    \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)),  \label{eqn:pderiv2}\\
  \pderiv{u_2}{x_1}(\xx) &= \Re (v'[\tau_2](x)) - 
    \Im (v''[\yy\cdot\eeta](x)) + \Im (v'[\eta_1](x)) +
    x_1\Im (v''[\eta_1](x)) + x_2\Im (v''[\eta_2](x)), \\
  \pderiv{u_2}{x_2}(\xx) &= -\Im (v'[\tau_2](x)) - 
    \Re (v''[\yy\cdot\eeta](x)) + x_1\Re (v''[\eta_1](x)) +
    \Im (v'[\eta_2](x)) + x_2\Re (v''[\eta_2](x)).
\end{align}
{\color{red}
Here we derive the equations~\eqref{eqn:pderiv1}-\eqref{eqn:pderiv2} 
and the other two are similar.
To derive equations~\eqref{eqn:pderiv1} and \eqref{eqn:pderiv2}, 
we need to apply the fact that if a real function $u$ is equivalent to 
the real part of a complex varaible function $f$, 
then we have $\nabla u=(\Re(f'),-\Im(f'))$.
Let $f_1(x)= v[\tau_1](x)$, $f_2(x)=v'[\yy\cdot\eeta](x)$, $f_3(x)=v'[\eta_1](x)$,
and $f_4(x)= v'[\eta_2](x)$. Then we can rewrite equation~\eqref{eqn:cauchy1}
\begin{align*}
u_1(\xx)&= u_{11}(\xx) +  u_{12}(\xx) +u_{13}(\xx)+u_{14}(\xx) \\
&=\Re (f_1(x)) + \Re (f_2(x))-x_1\Re (f_3(x)) - x_2\Re (f_4(x)).
\end{align*}
To get the gradient of $u_1(x)$, we have
\begin{align*}
\nabla u_1(x)&= \nabla u_{11}(x)+\nabla  u_{12}(x) 
+\nabla u_{13}(x)+\nabla u_{14}(x) \\ \\
&=\begin{bmatrix}
\Re(f_1'(x))\\ \\
-\Im(f_1'(x))
\end{bmatrix}+
\begin{bmatrix}
\Re(f_2'(x))\\ \\
-\Im(f_2'(x))
\end{bmatrix}
+
\begin{bmatrix}
-\Re(f_3(x))-x_1\Re(f_3'(x))\\ \\
x_1\Im(f_3'(x))
\end{bmatrix}
+
\begin{bmatrix}
-x_2\Re(f_4'(x))\\ \\
-\Re(f_4(x))+x_2\Im(f_4'(x))
\end{bmatrix}\\ \\
&=
\begin{bmatrix}
\Re (v'[\tau_1](x)) + 
    \Re (v''[\yy\cdot\eeta](x)) - \Re (v'[\eta_1](x)) - 
    x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x))\\ \\
- \Im (v'[\tau_1](x)) - 
    \Im (v''[\yy\cdot\eeta](x)) + x_1\Im (v''[\eta_1](x)) - 
    \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x))
\end{bmatrix}.
\end{align*}

}
\todo[inline]{S-H: last term seems to be missing an $x_1$.  Some of the
other terms seem to be a bit off.  It might be partially my fault from
when I updated some of the tex.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Vorticity}
Having calculated all derivatives of the double-layer potential, the
vorticity can written in terms of Cauchy integrals.  In particular
{\color{red}
\begin{align}
  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
\Re (v'[\tau_2](x)) + \Im (v'[\tau_1](x)) 
 + \Re (v'[\eta_2](x))+ \Im (v'[\eta_1](x)).
\end{align}
}
\todo[inline]{For S-H to fill in}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barycentric Quadrature for $v''(x)$}
While accurate quadrature rules for $v(x)$ and $v'(x)$ have already been
developed~\cite{bar-wu-vee2015}, this work requires a similar quadrature
rule for $v''(x)$.  We mimic the approach developed
in~\cite{bar-wu-vee2015} by starting with the Cauchy integral identities
{\color{red}
\begin{alignat}{3}
1 &= \frac{1}{2\pi i}\int_{\Gamma} 
    \frac{1}{y-x} dy, &&x \in \Omega, \label{eqn:cauchyId1}\\
\frac{1}{x-a} &= \frac{-1}{2\pi i}\int_{\Gamma} 
    \frac{(y-a)^{-1}}{y-x} dy,  \quad &&x \in \Omega^c\label{eqn:cauchyId2}. 
\end{alignat}
and the contour integral 
\begin{align}\label{eqn:cauchyId3}
0=\oint_{\Gamma} \frac{1}{(y-x)^n}dy, \quad n \neq 1.
\end{align}
Then we apply equations~\eqref{eqn:cauchyId1} and~\eqref{eqn:cauchyId3} on
the second derivative of Cauchy integral in \eqref{eqn:cauchy} and get
\begin{align*}
0 &= \frac{1}{2\pi i} \int_{\Gamma}
    \frac{2v^-(y)}{(y - x)^3} \, dy -v''(x)\\
&= \frac{1}{2\pi i} \int_{\Gamma}
    \frac{2v^-(y)}{(y - x)^3} \, dy 
-v''(x)\frac{1}{2\pi i}\int_{\Gamma} 
    \frac{1}{y-x} dy\\
&= \frac{1}{2\pi i} \int_{\Gamma}
    \frac{2v^-(y)}{(y - x)^3} \, dy 
-\frac{1}{2\pi i}\int_{\Gamma} 
    \frac{(y-x)^2v''(x)}{(y-x)^3} dy
-\frac{1}{2\pi i}\int_{\Gamma} \frac{2v(x)}{(y-x)^3}dy
-\frac{1}{2\pi i}\int_{\Gamma} \frac{2(y-x)v'(x)}{(y-x)^3}dy\\
&= \frac{1}{2\pi i}\int_{\Gamma} 
    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy.
\end{align*}
}
\todo[inline]{S-H: How do we get these identities?}
\begin{alignat}{3}
  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy, &&x \in \Omega, \\
  0 &= \frac{1}{2\pi i}\int_{\Gamma}
    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
\end{alignat}
{\color{red}
and the quadrature formulations are
\begin{alignat}{3}
  v''(x) &\approx
    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
\end{alignat}
where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.
